Appendix 4: Species distribution model comparison between INLA and sdmTMB

### 2022-01-05 doc/appendix-binomial-inla.Rmd
Tweak inlabru prediction

```{r inla-pred, out.width="6in"}
# pxl <- pixels(spde$mesh)
# pred_bru <- predict(m_bru, pxl)

nd_bru <- nd
sp::coordinates(nd_bru) <- c("X", "Y")
nd_bru <- as(nd_bru, "SpatialPointsDataFrame")
pred_bru <- predict(m_bru, nd_bru)

# ggplot(d) +
#   geom_point(aes(X, Y, colour = ??), size = 2) +
#   facet_wrap(~year) +
#   scale_colour_viridis_c() +
#   coord_fixed()
```

>>>>

```{r inla-pred, out.width="6in"}
nd_bru <- nd
nd_bru <- dplyr::left_join(nd_bru, yr_lu)
sp::coordinates(nd_bru) <- c("X", "Y")
nd_bru <- as(nd_bru, "SpatialPixelsDataFrame")
pred_bru <- predict(m_bru, data = nd_bru)

nrow(pred_bru$Predictor)
```
